Basic regression in Gaussian processes

### 2019-11-05 notebook/complete-discrete-version.Rmd
weaker ghost re-run, shorter runtime.

true_a <- 27.4      ### 21.5
believe_a <- 28.5 # 28.5   ### 22.5

@@

df %>%
  ggplot(aes(x, f)) + 
    geom_point(aes(col = a), alpha = 0.1) + 
    geom_line(aes(lty = group), data = df %>% filter(a == true_a | a == believe_a), 
              lwd = 1, show.legend = FALSE) +
    geom_hline(aes(yintercept = 0))

@@

```{r}
x0 <- which.min(abs(states - 5))
Tmax <- 700
```

@@

```{r}
set.seed(12345)
Tmax_learning <- 500
mdp_learning_ <- memoise::memoise(mdp_learning)
  learning_sim <- mdp_learning_(transition, reward, discount, 
                      x0 = x0, 
                      Tmax = Tmax_learning, 
                      true_transition = transition[[true_i]],
                      model_prior = prior,
                      type = "value iteration", 
                      epsilon = 1e-2)

@@

```{r mcmc, cache=TRUE}
if(!file.exists("samples.tsv.gz")){ # Manually cache the slow step

@@

readr::write_tsv(samples, "samples.tsv.gz")

} else {
  samples <- readr::read_tsv("samples.tsv.gz")
}
```

>>>>

true_a <- 27      ### 21.5
believe_a <- 28.5 # 28.5   ### 22.5

@@

df %>%
  ggplot(aes(x, f)) + 
    geom_point(aes(col = a), alpha = 0.8) + 
    geom_line(aes(lty = group), data = df %>% filter(a == true_a | a == believe_a), 
              lwd = 1, show.legend = FALSE) +
    geom_hline(aes(yintercept = 0)) + scale_color_viridis_c()

@@

```{r}
x0 <- which.min(abs(states - 5))
Tmax <- 200
```

@@

```{r}
set.seed(12345)
Tmax_learning <- 50
mdp_learning_ <- memoise::memoise(mdp_learning)
  learning_sim <- mdp_learning_(transition, reward, discount, 
                      x0 = x0, 
                      Tmax = Tmax_learning, 
                      true_transition = transition[[true_i]],
                      model_prior = prior,
                      type = "value iteration", 
                      epsilon = 1e-2)

@@

```{r mcmc, cache=TRUE}

@@
